### 2017-12-29 article.tex
adjustment

\begin{table}[H]	
\begin{center}
\begin{tabular}{ |l|l| }
	\hline
	\multicolumn{2}{|c|}{\textbf{Board of Directors}} \\
	\hline
	Richard Qiangdong Liu	&		Chairman and Chief Executive Officer \\
	\rowcolor[gray]{.95}
	Martin Chiping Lau		& 		Director\\
	Ming Huang				&		Independent Director \\
	\rowcolor[gray]{.95}
	Louis T. Hsieh			&		Independent Director \\
	David Daokui Li			&		Independent Director \\
	\hline
\end{tabular}
\end{center}
\caption{Board of directors of JD.com, Inc}\label{table:1}
\end{table}

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{|p{5.6cm}|r|r|r|r|}\hline
			&\multicolumn{2}{c|}{\textbf{Ordinary shares}}&\multicolumn{2}{c|}{\textbf{Treasury stock}}\\
			\hline
			&\multicolumn{1}{c|}{Shares}&Amount&\multicolumn{1}{c|}{Shares}&Amount\\
			\hline
		\rowcolor[gray]{.95}	
		Balance as of
		December 31,
		2015&2,793,756,650&358&(51,766,164)&(3)\\
		Issuance of ordinary shares&144,952,250&19&-&-\\
		\rowcolor[gray]{.95}
		Surrender of ordinary shares by certain	shareholder&(1)&-&-&-\\
		Exercise of sharebased	awards&-&-&2,820,648&77,496\\
		\rowcolor[gray]{.95}
		Share-based	compensation and vesting of sharebased	awards&-&-&8,812,582&78,903\\
		Balance as of December 31, 2016&2,938,708,899&377&(102,264,502)&(5,181,880)\\
			\hline
		\end{tabular}
	\end{center}
	\caption{Share capital (amounts in thousands of RMB \textyen, shares in one)}\label{table:1}
\end{table}

@@

In December 2014, the Group acquired 6.5\% equity interest in Tuniu with cash consideration of RMB305,930 (“Initial Investment”). Tuniu is a leading
online leisure travel company in China that is listed on the Nasdaq. The Group accounted for the Initial Investment as an available-for-sale security\footnote{F 41}.

>>>>

\begin{table}[H]	
\begin{center}
\begin{tabular}{ l|l }
	\hline
	\multicolumn{2}{c}{\textbf{Board of Directors}} \\
	\hline
	Richard Qiangdong Liu	&		Chairman and Chief Executive Officer \\
	\rowcolor[gray]{.95}
	Martin Chiping Lau		& 		Director\\
	Ming Huang				&		Independent Director \\
	\rowcolor[gray]{.95}
	Louis T. Hsieh			&		Independent Director \\
	David Daokui Li			&		Independent Director \\
	\hline
\end{tabular}
\end{center}
\caption{Board of directors of JD.com, Inc}\label{table:1}
\end{table}

@@

\renewcommand{\arraystretch}{0.83}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{5.6cm}rrrr}
			\toprule 
			& \multicolumn{2}{c}{\textbf{Ordinary shares}} & \multicolumn{2}{c}{\textbf{Treasury stock}} \\\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
			\multirow{-2}{*}{} &\multicolumn{1}{c}{Shares}&Amount&\multicolumn{1}{c}{Shares}&\multicolumn{1}{c}{Amount}\\
		\midrule
		\rowcolor[gray]{.96}	
		Balance as of
		December 31,
		2015&2,793,756,650&358&(51,766,164)&(3)\\
		Issuance of ordinary shares&144,952,250&19&-&-\\
		\rowcolor[gray]{.96}
		Surrender of ordinary shares by certain	shareholder&(1)&-&-&-\\
		Exercise of sharebased	awards&-&-&2,820,648&77,496\\
		\rowcolor[gray]{.96}
		Share-based	compensation and vesting of sharebased	awards&-&-&8,812,582&78,903\\
		Balance as of December 31, 2016&2,938,708,899&377&(102,264,502)&(5,181,880)\\
		\bottomrule
		\end{tabular}
	\end{center}
	\caption{Share capital (amounts in thousands of RMB \textyen, shares in one)}\label{table:1}
\end{table}

@@

In December 2014, the Group acquired 6.5\% equity interest in Tuniu with cash consideration of RMB305,930 (“Initial Investment”). Tuniu is a leading
online leisure travel company in China that is listed on the Nasdaq. The Group accounted for the Initial Investment as an available-for-sale security\footnote{See JD.com, Inc. annual report 2016, Page F 41}.
